---
title: "Formula E and Electric Vehicles"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Formula E vs Electric vehicles

Is there a correlation between searches for "Formula E" and "Electric vehicles" on Google?

First we download a data files from [Google Trends](https://www.google.co.uk/trends/explore?date=all&q=Formula%20E,electric%20vehicles)
- [us-searches](raw_data/us-searches.csv), containing searches for the US only. I think this is the chart used in the graphic shared.

```{r us}
# read in the US data
usSearches <- read.csv("raw_data/us-searches.csv")
names(usSearches) <- c("month", "fe", "electric")

# What is the correlation between the two searches?
cor.test(usSearches$fe, usSearches$electric)
```

Not really. What we care about above is the final number output, which tells us there's a correlation of -0.278 between the two, suggesting that when searches for one term increase, searches for the other decrease.

```{r echo=F}
library(lubridate); library(dplyr)
usSearches$month <- paste0(usSearches$month, "-01")
usSearches$month <- ymd(usSearches$month)
```


## What about after June 2014, shortly before Formula E began?
```{r us-recent}
# Filter the data to 
recentUS <- usSearches %>% filter(month >= "2014-06-01")

# What is the correlation between the two searches?
cor.test(recentUS$fe, recentUS$electric)
```
This time around, our correlation test tells us that the correlation is 0.326 ("medium", according to [Cohen's rule of thumb](http://staff.bath.ac.uk/pssiw/stats2/page2/page14/page14.html)). However, since our 95% confidence intervals include the number 0, we can't say with any real confidence that the correlation is not 0.

There does not appear to be any significant correlation between searches for Formula E and Electric vehicles.
